\documentclass[10pt,a4paper,ragged2e]{altacv}
\usepackage{xcolor}
\usepackage{transparent}
\usepackage[dvipsnames]{xcolor}
\geometry{left=1cm,right=9cm,marginparwidth=6.5cm,marginparsep=1.25cm,top=1.4cm,bottom=1.4cm}

\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\usepackage[hidelinks]{hyperref}
\usepackage{tcolorbox}

\definecolor{iconblue}{HTML}{1A73E8}
\definecolor{GoogleBlue}{HTML}{4285F4}
\definecolor{GoogleRed}{HTML}{EA4335}
\definecolor{GoogleYellow}{HTML}{FBBC05}
\definecolor{GoogleGreen}{HTML}{34A853}
\newcommand{\googletext}{\textbf{\textcolor{GoogleBlue}{G}\textcolor{GoogleRed}{o}\textcolor{GoogleYellow}{o}\textcolor{GoogleBlue}{g}\textcolor{GoogleGreen}{l}\textcolor{GoogleRed}{e}}}
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{CVLightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{black}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\newcommand{\skillcategory}[2]{%
  \smallskip
  \noindent\colorbox{VividPurple!15}{%
    \textcolor{VividPurple}{#1}\;\textbf{\small #2}%
  }%
  \smallskip
}

\newcommand{\ptag}[1]{\colorbox{VividPurple!12}{\tiny\textcolor{VividPurple}{#1}}\,}

\newcommand{\cvproject}[6]{%
  \noindent\textcolor{VividPurple}{\textbf{\small #1}}\enspace{\footnotesize\textcolor{SlateGrey}{\href{#2}{\faGithub\,\texttt{Code}}}\enspace\textcolor[HTML]{FF9D00}{\href{#3}{\faExternalLink\,\texttt{Demo}}}\enspace\textcolor[HTML]{1A7F5A}{\href{#4}{\faBook\,\texttt{Docs}}}}\vspace{1pt}\\
  \noindent{\small #5}\vspace{1pt}\\
  \noindent#6
  \vspace{3pt}{\color{VividPurple!20}\hrule}\vspace{6pt}
}

\newcommand{\cvprojectnogit}[6]{%
  \noindent\textcolor{VividPurple}{\textbf{\small #1}}\enspace{\footnotesize\textcolor[HTML]{1A7F5A}{\href{#4}{\faBook\,\texttt{Docs}}}}\vspace{1pt}\\
  \noindent{\small #5}\vspace{1pt}\\
  \noindent#6
  \vspace{3pt}{\color{VividPurple!20}\hrule}\vspace{6pt}
}

\newcommand{\cvlink}[4]{%
  \noindent
  \begin{tcolorbox}[enhanced,colback=VividPurple!8,colframe=VividPurple!40,boxrule=0.4pt,arc=3pt,left=4pt,right=4pt,top=2pt,bottom=2pt,before skip=3pt,after skip=3pt]
    \textcolor{VividPurple}{#1}\;\textbf{\small #2}\\[1pt]
    \textcolor{CVLightGrey}{\scriptsize\href{#3}{#4}}
  \end{tcolorbox}%
}

\begin{document}
\name{Mohammad Noorchenarboo}
\tagline{AI Researcher | PhD Candidate in Computer Engineering | Statistician}

\personalinfo{%
  \email{mohammadnoorchenarboo@gmail.com}
  % \linkedin{\href{https://www.linkedin.com/in/mnoorchenar}{linkedin.com/in/mnoorchenar}}
  \homepage{\href{https://mnoorchenar.github.io/}{mnoorchenar.github.io}}
  \googlescholar{\href{https://scholar.google.com/citations?user=nn_Toq0AAAAJ}{Google Scholar}}
  \location{Western University, Ontario, Canada}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

%% ===================== PAGE 1 SIDEBAR =====================
\marginpar{\vspace*{\dimexpr1pt-\baselineskip}\raggedright
\vspace{5mm}

\cvsection{\fontsize{14}{12}\selectfont Research Profile}
PhD candidate in Computer Engineering with interdisciplinary training in AI, statistics, biostatistics, and industrial engineering. Research centers on developing advanced deep learning and machine learning methods for complex real-world systems, including multimodal architectures, transformer-based models, and time-series predictive frameworks. A major focus is explainable and trustworthy AI --- making complex models more transparent, robust, and suitable for high-stakes applications in healthcare and energy systems. Author of 10+ publications in venues including \textit{Surgical Endoscopy}, \textit{Energy and Buildings}, \textit{JMIR}, and IEEE.\par

\vspace{3mm}
\cvsection{\fontsize{14}{12}\selectfont Research Interests}

\noindent\textcolor{VividPurple}{\footnotesize\faBrain\;\textbf{Large Language Models \& Generative AI}}
\smallskip

\cvtag{LLM Fine-Tuning}
\cvtag{Foundation Models}
\cvtag{Retrieval-Augmented Generation}

\smallskip
\noindent{\color{CVLightGrey!60}\dotfill}
\smallskip

\noindent\textcolor{VividPurple}{\footnotesize\faSearch\;\textbf{Explainable \& Trustworthy AI}}
\smallskip

\cvtag{Model Interpretability}
\cvtag{Responsible AI}

\smallskip
\noindent{\color{CVLightGrey!60}\dotfill}
\smallskip

\noindent\textcolor{VividPurple}{\footnotesize\faSitemap\;\textbf{Representation Learning \& Data Fusion}}
\smallskip

\cvtag{Multimodal Learning}
\cvtag{Transformer Architectures}
\cvtag{Self-Supervised Learning}

\smallskip
\noindent{\color{CVLightGrey!60}\dotfill}
\smallskip

\noindent\textcolor{VividPurple}{\footnotesize\faLineChart\;\textbf{Predictive Modeling \& Forecasting}}
\smallskip

\cvtag{Deep Learning}
\cvtag{Time-Series Analysis}
\cvtag{Anomaly Detection}

\vspace{-1mm}
\cvsection{\fontsize{14}{12}\selectfont Links}
\cvlink{\faGlobe}{Portfolio}{https://mnoorchenar.github.io/}{mnoorchenar.github.io}
\cvlink{\faCode}{Projects}{https://mnoorchenar.github.io/projects}{mnoorchenar.github.io/projects}
\cvlink{\faBarChart}{Teaching Dashboard}{https://mnoorchenar.github.io/teaching-dashboard/}{mnoorchenar.github.io/teaching-dashboard}
}

%% ===================== PAGE 1 MAIN COLUMN =====================
\vspace{1mm}
\cvsection{Education}

\cvevent{\textbf{Ph.D.} Computer Engineering}{}{2022 -- 2026}{Western University, London, Ontario, Canada}
\vspace{-1mm}
\begin{itemize}
\item \textbf{Dissertation:} Advanced deep learning models for complex real-world systems, focused on explainability and deployment in high-stakes applications.
% \item \textbf{Supervisor:} Dr. Katarina Grolinger (Canada Research Chair Tier 2, Engineering Applications of ML)
\item \textbf{GPA:} 93.75/100
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faTrophy\ \textbf{Scholarships:}} Danny Ho Software Engineering Scholarship (\$10,000, 2025);
\hspace*{15mm} Graduate Scholarship in Engineering and Science (\$1,000, 2026)
\item[] \hspace*{-1.4\leftmargin} \textcolor{VividPurple}{\faInstitution\ \textbf{Industry Partnerships:}} London Health Sciences Centre --- predictive modeling and clinical NLP from large-scale EHR data; London Hydro (NSERC-funded), explainability and anomaly detection in time-series energy systems.
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faBook\ \textbf{Publications:}} 4 published --- \textit{Surgical Endoscopy} (2025), \textit{Int. J. Medical Informatics} (2026), \textit{Energy and Buildings} (2025), IEEE \textit{IECON 2024}; 3 under review in \textit{BMC Anesthesiology}, \textit{Engineering Applications of AI}, and \textit{Applied Energy}.
\end{itemize}

\vspace{-7pt}
\divider

\cvevent{\textbf{M.Sc.} Biostatistics}{}{2019 -- 2022}{Tehran University of Medical Sciences, School of Public Health, Tehran, Iran}
\begin{itemize}
\item \textbf{Thesis:} Statistical methods for genetic epidemiology and clinical cohorts.
% \item \textbf{Supervisor:} Dr. Mehdi Yaseri (Professor, Epidemiology and Biostatistics)
\item \textbf{GPA:} 97.55/100
\item \textbf{Specialization:} Survival analysis, regression modeling, longitudinal data analysis, clinical trial methods, and epidemiologic statistics.
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faStar\ \textbf{National Rankings:}} 5th (M.Sc., 2019) $\cdot$ 4th (Ph.D., 2018) --- nationwide among 1,000+ candidates.
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faInstitution\ \textbf{Industry Partnership:}} Endocrinology and Metabolism Research Institute (EMRI) --- GWAS on 663K+ SNPs; metabolomics profiling of 50 plasma metabolites for ASCVD risk; statistical analysis of a 3-arm CABG RCT.
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faBook\ \textbf{Publications:}} 3 papers in \textit{JMIR}, \textit{Frontiers in Cardiovascular Medicine}, and \textit{J. Biostatistics and Epidemiology}.
\end{itemize}

\vspace{-7pt}
\divider

\cvevent{\textbf{M.Sc.} Industrial Engineering}{}{2013 -- 2015}{Iran University of Science and Technology (IUST), Tehran, Iran}
\begin{itemize}
\item \textbf{Thesis:} Advanced statistical process control methods for quality engineering and monitoring of complex industrial systems.
\item \textbf{Specialization:} Optimization of complex processes and systems, including supply chain management, production systems, and operations research.
\item \textbf{GPA:} 86.30/100
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faStar\ \textbf{National Ranking:}} 84th among 10,000 candidates.
\end{itemize}

\vspace{-7pt}
\divider

\cvevent{\textbf{B.Sc.} Statistics}{}{2009 -- 2013}{Ferdowsi University of Mashhad, Mashhad, Iran}
\vspace{-1mm}
\begin{itemize}
\item \textbf{GPA:} 74.20/100 overall; 88.25/100 final two years.
\end{itemize}

\vspace{3.5pt}

\cvsection{Teaching Experience}
\vspace{-2pt}
\cvevent{}{Professor}{May 2024 -- Present}{Fanshawe College, School of Information Technology, London, ON, Canada}

{\small Teaches \textbf{15 graduate-level Deep Learning courses} over 5 semesters (\textasciitilde450 total enrollments). Covers CNN, RNN, Transformer, ViT, Diffusion, and LLM (BERT, GPT) architectures; integrates XAI methods. Mentors capstone projects in real applications. Course satisfaction grew \textbf{+32.8\% over 5 semesters}.}

\vspace{1mm}
\begin{itemize}
\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faBook\ \textbf{Courses Taught:}} Data Science \& ML $\cdot$ ML Optimization Strategies $\cdot$ TensorFlow \& Keras $\cdot$ Deep Learning with TensorFlow \& Keras
{\fontsize{8.5}{10}\selectfont\item[] \hspace*{-1.35\leftmargin} \textcolor{VividPurple}{\faStar\ \textbf{Teaching Evaluation:}} Composite score \textbf{4.90/5.00} across 20 competencies --- \textbf{+0.27 above college average} (4.63) and \textbf{+0.34 above School of IT average} (4.56); overall effectiveness rating \textbf{4.96/5.00}, surpassing college average by +0.55.}
\end{itemize}

\clearpage

%% ===================== PAGE 2 SIDEBAR =====================
\marginpar{\vspace*{\dimexpr1pt-\baselineskip}\raggedright
\vspace{3mm}

\cvsection{\fontsize{11}{12}\selectfont Invited Talks}
\begin{itemize}
\item[] \textcolor{VividPurple}{\faMicrophone}\;\googletext\;\textbf{Event Speaker} -- Presented on generative AI and real-world applications at Google conferences, London, ON, Canada.\emph{ (2025)}
\item[] \textcolor{VividPurple}{\faBullhorn}\;\textbf{Rock IT Speaker} -- AI lecture for secondary students, Fanshawe College \emph{(2025)}
\end{itemize}

\vspace{-1mm}
\cvsection{\fontsize{11}{12}\selectfont Academic Service}
\noindent\textcolor{VividPurple}{\faSearch\;\textbf{Journal Reviewer}}
\smallskip
\begin{itemize}
\item[] {\textit{IEEE Transactions on Industrial Informatics} \\ \textcolor{CVLightGrey}{2025 -- present}}
\item[] {\textit{Journal of Biostatistics and Epidemiology} \\ \textcolor{CVLightGrey}{2019 -- 2022}}
\end{itemize}

\vspace{-1mm}
\cvsection{\fontsize{10}{12}\selectfont Workshops Delivered}
\begin{itemize}
\item[] \textcolor{VividPurple}{\faBarChart}\;\textbf{SPSS Workshops} -- TUMS School of Public Health (May 2019) and FARABI Eye Hospital, TUMS (Apr 2020).
\item[] \textcolor{VividPurple}{\faSitemap}\;\textbf{SEM Workshop (R \& LISREL)} -- Latent variable modeling, TUMS Dept.\ of Epidemiology (Apr 2019).
\item[] \textcolor{VividPurple}{\faCogs}\;\textbf{MINITAB Workshop} -- Statistical process control, IUST Dept.\ of Industrial Engineering (Oct 2016).
\end{itemize}

\cvsection{\fontsize{12}{12}\selectfont Selected Projects}
\vspace{-1mm}
\cvproject{Production ML Risk Dashboard for Banking \& Insurance}{https://github.com/mnoorchenar/risksight-pro}{https://huggingface.co/spaces/mnoorchenar/risksight-pro}{https://mnoorchenar.github.io/projects/Projects-Files/008-risksight-pro.html}{A full-stack banking and insurance risk intelligence platform unifying 7 ML-powered modules --- credit scoring, fraud detection, VaR/CVaR, loan portfolio, claims, underwriting, and loss ratio --- with 3 live Scikit-learn models and 3 REST scoring endpoints.}{\ptag{Flask}\ptag{Credit Risk}\ptag{Fraud Detection}\ptag{VaR/CVaR}\ptag{Risk Analytics}}

\cvproject{Full-Stack Statistical Experimentation, A/B Testing Platform}{https://github.com/mnoorchenar/experiment-lab}{https://huggingface.co/spaces/mnoorchenar/experiment-lab}{https://mnoorchenar.github.io/projects/Projects-Files/011-experiment-lab.html}{A full-stack statistical experimentation suite covering the complete experiment lifecycle --- power analysis with MDE curves; A/B testing via z-test and Welch's t-test with a dual-gate significance verdict; two-way factorial ANOVA with interaction; and Monte Carlo sequential testing comparing peeking-problem inflation vs O'Brien-Fleming correction.}{\ptag{Power Analysis}\ptag{DoE}\ptag{Sequential Testing}\ptag{SciPy}\ptag{statsmodels}\ptag{Flask}}

\cvproject{Five-Agent LangGraph Document Research System}{https://github.com/mnoorchenar/docmind}{https://huggingface.co/spaces/mnoorchenar/docmind}{https://mnoorchenar.github.io/projects/Projects-Files/013-docmind.html}{A five-agent document research system built on LangGraph 0.2 StateGraph --- Planner, Retriever, Grader, Generator, and Critic --- using only 3 LLM calls per query; score-based Grading cuts latency by 60\%; hybrid FAISS + BM25 + RRF improves top-5 recall by +18\%; cited answers with hallucination detection; PDF and URL ingestion.}{\ptag{Agentic AI}\ptag{LangChain}\ptag{RAG}\ptag{FAISS}\ptag{BM25}\ptag{Hallucination Detection}}

\begin{center}
{\raisebox{0.15ex}[0pt][0pt]{%
\colorbox{OliveGreen!12}{%
\hspace{1pt}\small\textcolor{OliveGreen}{\faCode\ \href{https://mnoorchenar.github.io/projects}{All Projects}}\hspace{3pt}%
}}}
\end{center}
}

%% ===================== PAGE 2 MAIN COLUMN =====================
\vspace{-2mm}
\cvsection{Teaching Experience \small\textcolor[rgb]{0.4,0.4,0.4}{(continued)}}

\cvevent{}{Teaching Assistant}{Sep 2022 -- Present}{Western University, London, ON, Canada}

\vspace{-2mm}
{\small
\begin{itemize}
\item DATASCI 3000A/B: Intro to Machine Learning (×2)
\item Software Project \& Process Management
\item SE2250B: Software Construction
\item Scripting Programming Language Fundamentals
\item Software Design for Systems Engineering
\item Programming Fundamentals for Engineers
\end{itemize}
}
\vspace{-2mm}
\divider

\cvevent{}{Teaching Assistant}{Sep 2020 -- Jan 2021}{Tehran University of Medical Sciences}

\vspace{-2mm}
{\small Biostatistical Methods --- hands-on workshops in R, SPSS, and MINITAB for graduate biostatistics students.}

\vspace{1mm}

\cvsection{Publications}\hfill
{\raisebox{0.25ex}[0pt][0pt]{%
\colorbox{blue!10}{%
\small\textcolor{blue}{\faGraduationCap\ \href{https://scholar.google.ca/citations?user=nn_Toq0AAAAJ&hl=en}{Full list on Google Scholar}}%
}}}
\vspace{-0.7em}

\textcolor{VividPurple}{\faBook\ \textbf{Journal Articles}}
\begin{itemize}
\item Kwong, M., \textbf{Noorchenarboo, M.}, Grolinger, K., Hawel, J., Schlachta, C. M., Elnahas, A. \textit{Optimizing surgical efficiency: predicting case duration of common general surgery procedures using machine learning}. \textbf{Surgical Endoscopy}, 39(8), 5227--5234, 2025.

\item \textbf{Noorchenarboo, M.}, Kwong, M., Elnahas, A., Hawel, J., Schlachta, C. M., \& Grolinger, K. \textit{Benchmarking text encoding strategies in multimodal clinical data for surgical case duration prediction}. \textbf{International Journal of Medical Informatics}, 106416, 2026.

\item \textbf{Noorchenarboo, M.}, \& Grolinger, K. \textit{Explaining deep learning-based anomaly detection in energy consumption data by focusing on contextually relevant data}. \textbf{Energy and Buildings}, 328, 115177, 2025.

\item Dehghanbanadaki, H., Dodangeh, S., \textbf{Noorchenarboo, M.}, et al. \textit{Metabolomics profile and 10-year atherosclerotic cardiovascular disease (ASCVD) risk score}. \textbf{Frontiers in Cardiovascular Medicine}, 10, 1161761, 2023.

\item \textbf{Noorchenarboo, M.}, Akbarzadeh, M., Fahimfar, N., et al. \textit{Multivariate and gene-based association testing of sarcopenia: Bushehr Elderly Health Program (BEH)}. \textbf{Journal of Biostatistics and Epidemiology}, 8(2), 195--207, 2022.

\item Ghorbani, B., Jackson, A. C., \textbf{Noorchenarboo, M.}, et al. \textit{Comparing the effects of gamification and teach-back training methods on adherence to a therapeutic regimen in patients after coronary artery bypass graft surgery: randomized clinical trial}. \textbf{Journal of Medical Internet Research}, 23(12), e22557, 2021.

\item \textbf{Noorchenarboo, M.}, Mousavi, S. A., \& Moheimani, H. \textit{Country Level Socioeconomic and Health System Indicators Explain COVID-19 Mortality Worldwide}. \textbf{Journal of Biostatistics and Epidemiology}, 6(2), 93--100, 2020.
\end{itemize}

\vspace{-2mm}
\divider

\textcolor{VividPurple}{\faUsers\ \textbf{Conference Papers}}
\begin{itemize}
\item Danish, M. U., \textbf{Noorchenarboo, M.}, Narayan, A., Grolinger, K. \textit{ChebyRegNet: An unsupervised deep learning technique for deformable medical image registration}. \textbf{IECON 2024, IEEE Industrial Electronics Society}, 1--8, 2024.
\end{itemize}

\vspace{-2mm}
\divider

\textcolor{VividPurple}{\faClockO\ \textbf{Preprints \& Under Review}}
\begin{itemize}
\item \textbf{Noorchenarboo, M.}, Kwong, M., Grolinger, K., Elnahas, A. \textit{Multi-modal machine learning for prediction of post-anesthesia care unit recovery time}. \textbf{Research Square}, 2026. \textit{(Under review, BMC Anesthesiology)}

\item \textbf{Noorchenarboo, M.}, \& Grolinger, K. \textit{Temporal Deep Explainer: A model-agnostic feature attribution approach for interpretable time-series load forecasting}. \textbf{SSRN} 5500798, 2025. \textit{(Under major revision, Engineering Applications of AI)}

\item \textbf{Noorchenarboo, M.}, \& Grolinger, K. \textit{DEPICT: Explainable energy forecasting with pattern integration and temporal attention}. \textbf{SSRN} 5660227, 2026. \textit{(Under review, Applied Energy)}

{\fontsize{8.9}{8}\selectfont
\item Mousavi, S. A., \textbf{Noorchenarboo, M.}, \& Moheimani, H. \textit{Developing a Diagnostic Decision Support Tool with Machine Learning Classification Algorithms to Improve Breast Cancer Screening: A Cross-Sectional Study on Iranian Women}, 2021.
}
\end{itemize}

\clearpage

%% ===================== PAGE 3 SIDEBAR =====================
\marginpar{\vspace*{\dimexpr1pt-\baselineskip}\raggedright
\vspace{2mm}
\cvsection{Technical Skills}
\skillcategory{\faCode}{Languages \& Libraries}
\begin{itemize}
    \item Python (TensorFlow, Keras, PyTorch, scikit-learn, XGBoost, Plotly) (6+ years)
    \item R, R Markdown, R Shiny (10+ years)
    \item SQL (4+ years)
\end{itemize}
\smallskip
\skillcategory{\faCogs}{DevOps \& Tooling}
\begin{itemize}
    \item Docker (2+ years)
    \item GitHub (5+ years)
    \item Linux / Ubuntu (3+ years)
\end{itemize}
\smallskip
\skillcategory{\faBarChart}{Visualization \& Deployment}
\begin{itemize}
    \item Tableau, Power BI (1+ year)
    \item Flask, Streamlit (1+ year)
\end{itemize}
\smallskip
\skillcategory{\faFlask}{Statistical Software}
\begin{itemize}
    \item SPSS, MINITAB (10+ years)
    \item STATA (2+ years)
\end{itemize}
\vspace{2mm}
\cvsection{Analytical Skills}
\skillcategory{\faDatabase}{Deep Learning}
\begin{itemize}
    \item Recurrent: RNN, LSTM, GRU
    \item Convolutional: CNN, 1D-CNN, TCN
    \item Transformers: BERT, GPT, Vision Transformer, Temporal Fusion Transformer
\end{itemize}
\smallskip
\skillcategory{\faTree}{Machine Learning}
\begin{itemize}
    \item Tree-based: Random Forest, XGBoost, LightGBM, CatBoost, GBM
    \item Linear models, SVM, KNN, clustering, ensemble methods
\end{itemize}
\smallskip
\skillcategory{\faCogs}{Data Processing}
\begin{itemize}
    \item Feature engineering, ETL pipeline design
    \item Dimensionality reduction, class imbalance handling, multimodal data fusion
\end{itemize}
\smallskip
\skillcategory{\faSearch}{Explainability \& Fairness}
\begin{itemize}
    \item SHAP, LIME, attention-based interpretation
    \item Fairness and bias analysis for clinical models
\end{itemize}
\smallskip
\skillcategory{\faLineChart}{Experimental Design}
\begin{itemize}
    \item RCT analysis (ANOVA), A/B testing
    \item Power analysis, sample sizing
\end{itemize}
\smallskip
\skillcategory{\faBook}{NLP \& LLM}
\begin{itemize}
  \item Foundation Models: BERT, GPT
  \item LLM Fine-Tuning, Prompt Engineering, Knowledge Distillation
  \item RAG, Semantic Search, Hallucination Mitigation, Multi-Agent Systems
  \item LangChain, LangGraph
\end{itemize}
\smallskip
\skillcategory{\faFlask}{Generative Models}
\begin{itemize}
  \item Variational Autoencoder (VAE)
  \item Generative Adversarial Network (GAN)
  \item Diffusion Models
\end{itemize}
}

%% ===================== PAGE 3 MAIN COLUMN =====================
\vspace{-2mm}
\cvsection{Research \& Industry Experience}

\cvevent{}{Senior Data Scientist}{May 2023 -- Dec 2025}{London Health Sciences Centre Research Institute (LHSC), London, ON, Canada}
\begin{itemize}
\item Designed and deployed predictive ML pipelines on 180,000+ multimodal EHR records from 3 hospitals, benchmarking 8 architectures (XGBoost, LightGBM, ANN, TabTransformer) with feature engineering, 10-fold CV, and Bayesian optimization; best model achieved MAE=31.8 min with statistically zero bias ($-$0.37 min), outperforming domain-expert estimates by 18+ min.
\item Benchmarked 5 text-encoding strategies (TF-IDF, Label Encoding, Count Vectorizer, ClinicalBERT, Sentence-BERT) on 180,366 surgical operative notes fused with structured EHR features; Sentence-BERT reduced prediction error by 16\%; compressed ClinicalBERT (436 MB) by \textbf{99.25\%} via knowledge distillation and INT8/ONNX quantization achieving \textbf{43.7$\times$} faster inference (statistically equivalent accuracy, Wilcoxon + BH-FDR).
\item Deployed RAG systems and LLM-based clinical NLP on GPU-accelerated HPC with end-to-end ETL and MLOps/CI/CD pipelines; applied SHAP and attention-based interpretability with fairness and bias analysis across patient subgroups; delivered Plotly/Flask KPI dashboards to surgical and administrative stakeholders across 3 institutions.
\item Co-authored 3 papers: \textit{Surgical Endoscopy} (Q1, IF: 2.7, 2025), \textit{Int.\ J.\ Medical Informatics} (2026); 1 under review in \textit{BMC Anesthesiology}.
\end{itemize}

\vspace{-5pt}
\divider

\cvevent{}{Applied AI Scientist}{Nov 2022 -- Apr 2023}{London Hydro, London, Ontario, Canada \normalfont\textit{(NSERC-funded)}}
\begin{itemize}
\item Developed a context-aware XAI framework for anomaly detection in time-series smart-meter data, replacing random SHAP baselines with cosine-similarity-matched historical windows; achieved \textbf{38\% average reduction} in explanation variability across 10 DL architectures (LSTM, GRU, TCN, WaveNet, TFT) and 250+ combinations (up to 80.3\%, p$<$0.001); benchmarked 20+ forecasting architectures with end-to-end ML pipelines, SQL databases, and R Shiny/Flask dashboards.
\item 3 publications: \textit{Energy and Buildings} (IF: 7.1); under major revision in \textit{Engineering Applications of AI} (IF: 8.0); under review in \textit{Applied Energy} (IF: 11.5).
\end{itemize}

\vspace{-5pt}
\divider

\cvevent{}{Principal Data Scientist}{Jan 2020 -- Aug 2022}{Endocrinology and Metabolism Research Institute (EMRI), Tehran, Iran}
\begin{itemize}
\item Built scalable data pipelines and QC workflows for large-scale structured datasets (663K+ features, 2,772 participants); applied MultiPhen and GATES to genome-wide association data achieving up to 2$\times$ statistical power over single-trait GWAS baselines.
\item Profiled 50 plasma biomarkers in 1,102 participants via PCA and logistic regression, identifying 14 significant ASCVD predictors across 5 pathways; analyzed a 3-arm CABG RCT (n=123) confirming gamification outperformed teach-back on two primary outcomes.
\item Built automated R Markdown QC pipelines, R Shiny dashboards, SQL databases for research teams; contributed to 5 publications across \textit{JMIR}, \textit{Frontiers in Cardiovascular Medicine}, and \textit{J.\ Biostatistics and Epidemiology} ($\times$2).
\end{itemize}

\vspace{-5pt}
\divider

\cvevent{}{Senior Statistical Analyst}{Jan 2014 -- Feb 2018}{Moshaveran Iran Research Institute, Tehran, Iran}
\begin{itemize}
\item Delivered predictive ML and risk modeling solutions across banking, insurance, and retail (credit scoring, churn modeling, segmentation, demand forecasting); led statistical consulting across 500+ projects covering A/B testing, power analysis, meta-analysis, and survey analysis in R and SPSS.
\end{itemize}

\vspace{-5pt}
\divider

\cvevent{}{Statistical Programmer}{Mar 2013 -- Aug 2014}{Royan Stem Cell Technology Institute, Cord Blood Bank, Tehran, Iran}
\begin{itemize}
\item Developed statistical programs for biomedical data analysis ensuring data integrity and research compliance; translated complex statistical results into clear visualizations for interdisciplinary research teams.
\end{itemize}
\clearpage

\end{document}